Perimeter Control of Swarms

### 2019-01-08 paper.tex
Updates

The paper is structured as follows: Section~\ref{sec:RelatedWork} discusses related work. Section~\ref{sec:Baseline} introduces a baseline swarm model to allow comparisons of the algorithms presented in this paper. Section~\ref{sec:DestinationApp} discusses th mechanism used to add a directional bias to an agents movement. Section~\ref{sec:CoordRole} discusses the rules by which a coordinator is identified. Section~\ref{sec:AllAgents} discusses the effects of using a GPS directional bias when applied to all the agents. Section~\ref{sec:BasicCount} discusses the application of the basic count algorithm and its effects. Section~\ref{sec:complexMulti}
discusses full perimeter detection and it application. Section~\ref{sec:compareBaselineAll1} compares the effects of the algorithms to the baseline. Section~\ref{sec:EnergyReductionGPS} compares the energy savings of limiting the use of the GPS sensors in coordinating a swarm. Section~\ref{sec:MessagePropogation} discusses the issues associated with message propogation in the identification of perimeter types. Section~\label{sec:conclusion} highlights the findings and Section~\ref{sec:FutureWork} discusses additional applications of the techniques discussed within this paper.

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/SwarmPathBaseline.pdf}
\end{center}
\caption{Baseline swarm path\label{coord:SwarmPathBaseline1}}
\end{figure}

@@

\subsection{Baseline and effect of no perimeter detection\label{section:compareBaselineNoPerimeter}}
To identify the effect of the all-agents algorithm the simulation is executed using the same parameters as the baseline swarm with the added \textit{destination vector} on all the agents. The effect of introducing this bias on the swarms internal characteristics is shown in~Figures~\ref{reduced:BaselineAllAgentsMag1} and~\ref{reduced:BaselineAllAgentsDist1}.
%BASELINE-ALLAGENTS-MAG.py
\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllAgentsMag1.pdf}
\end{center}
\caption{Baseline/All agents comparison \textit{inter-agent vector} magnitude\label{reduced:BaselineAllAgentsMag1}}
\end{figure}

@@

%% \begin{algorithm}
%% \DontPrintSemicolon
%% \SetAlgoLined
%% \caption{CheckVisibility}
%% \KwData{b,angles}
%% \For{$i \leftarrow 0$ \KwTo $size(angles)-1$}{
%% 	\eIf{i == size(angles)-1}{
%% 		\If{$cosrule(b,angles[size(angles)-1][0],angles[i][0]$}{
%%    		\KwRet{True}
%%    	}
%% 	}
%% 	{\If{$cosrule(b,angles[i + 1][0],angles[i][0]$}{
%% 			\KwRet{True}
%% 		}
%% 	}
%% }
%% \KwRet{False}
%% \label{algo:checkVisibility}
%% \end{algorithm}

>>>>

The paper is structured as follows: Section~\ref{sec:RelatedWork} discusses related work. Section~\ref{sec:Baseline} introduces a baseline swarm model to allow comparisons of the algorithms presented in this paper. Section~\ref{sec:DestinationApp} discusses th mechanism used to add a directional bias to an agents movement. Section~\ref{sec:CoordRole} discusses the rules by which a coordinator is identified. Section~\ref{sec:AllAgents} discusses the effects of using a GPS directional bias when applied to all the agents. Section~\ref{sec:BasicCount} discusses the application of the basic count algorithm and its effects. Section~\ref{sec:complexMulti}
discusses full perimeter detection and it application. Section~\ref{sec:compareBaselineAll1} compares the effects of the algorithms to the baseline. Section~\ref{sec:EnergyReductionGPS} compares the energy savings of limiting the use of the GPS sensors in coordinating a swarm. Section~\ref{sec:MessagePropogation} discusses the issues associated with message propogation in the identification of perimeter types. Section~\ref{sec:conclusion} highlights the findings and Section~\ref{sec:FutureWork} discusses additional applications of the techniques discussed within this paper.

@@

% \begin{figure}
% \begin{center}
% \includegraphics[width=9cm]{figures/SwarmPathBaseline.pdf}
% \end{center}
% \caption{Baseline swarm path\label{coord:SwarmPathBaseline1}}
% \end{figure}

@@

\subsection{Baseline and effect of no perimeter detection\label{section:compareBaselineNoPerimeter}}
To identify the effect of the all-agents algorithm the simulation is executed using the same parameters as the baseline swarm with the added \textit{destination vector} on all the agents. The effect of introducing this bias on the swarms internal characteristics is shown in~Figures~\ref{reduced:BaselineAllAgentsMag1} and~\ref{reduced:BaselineAllAgentsDist1}.
%BASELINE-ALLAGENTS-MAG.py
% \begin{figure}
% \begin{center}
% \includegraphics[width=9cm]{figures/BaselineAllAgentsMag1.pdf}
% \end{center}
% \caption{Baseline/All agents comparison \textit{inter-agent vector} magnitude\label{reduced:BaselineAllAgentsMag1}}
% \end{figure}

@@
